Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-12-01 manuscript_thev_transcriptome.Rmd
validated tplE3 and E3-trxptA juncs

### RNA extraction and Sequencing   
Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` as per manufacturer's instructions. An agarose gel electrophoresis was performed to check RNA integrity. The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2. Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`. Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.

### Validation of Novel Splice Junctions 
All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work. However, these predicted splice junctions have not been experimentally validated hitherto, and we identified additional novel exons, giving a more complete picture of the transcripts.
~~The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in Table###1~~. We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit paired with their respective universal primers (~~supplementary, PCR methods~~). Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site. After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR experiment, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method and Sanger sequenced to validate these splice junctions at the sequence level.

### 3' Rapid Amplification of cDNA Ends (3'RACE)

>>>>

### RNA extraction and Sequencing   
Total RNA was extracted from infected cells using Thermofishers' RNAqueous™-4PCR Total RNA Isolation Kit `(#AM1914)` per manufacturer's instructions. An agarose gel electrophoresis was performed to check RNA integrity. The RNA quantity and purity was initially assessed using `nanodrop`, and RNA was used only if the A260/A280 ratio was 2.0 ± 0.05 and the A260/A230 ratio was >2 and <2.2. Extracted total RNA samples were sent to `LC Sciences, Houston TX` for poly-A-tailed mRNA sequencing where RNA integrity was checked with `Agilent Technologies 2100 Bioanalyzer High Sensitivity DNA Chip` and poly(A) RNA-seq library was prepared following `Illumina's TruSeq-stranded-mRNA sample preparation protocol`. Paired-end sequencing was performed on `Illumina's NovaSeq 6000 sequencing system`.

### Validation of Novel Splice Junctions 
All splice junctions identified in this work are novel except one predicted splice site each for pTP and DBP, which were corroborated in our work. However, these predicted splice junctions had not been experimentally validated hitherto, and we identified additional novel exons, giving the complete picture of these transcripts.
~~The novel splice junctions after consolidating all transcripts with `StringTie` which we validated by PCR and Sanger Sequencing are shown in Table###1~~. We designed primers that crossed a range of novel exon–exon boundaries for each specific transcript in a transcription unit paired with their respective universal primers (~~supplementary, PCR methods~~). Each forward primer contained a KpnI restriction site and reverse primers, an XbaI site. After first-strand cDNA synthesis with SuperScript™ III First-Strand Synthesis System (ThermoFisher SCIENTIFIC), these primers were used in a targeted PCR, the PCR products were analysed on Agarose gels, cloned by traditional restriction enzyme method, and Sanger sequenced to validate these splice junctions at the sequence level.

### 3' Rapid Amplification of cDNA Ends (3'RACE)  
We performed a rapid amplification of sequences from the 3′ ends of mRNAs (3'-RACE) experiment with total RNA extracted from independently infected MDTC-RP19 cells following the protocol described by Green _et al_ [@Green2019] with modifications. Briefly,
